### 2016-07-28 Theorem1_FP.tex
Corrections Proof1

\heading{Linear-PRF construction. }
Here we consider a hash-based filter that was attacked by Neidermayer et al. in~\cite{xxx}.  Let $B_{\mathrm{lin}}=(\Hash,\Rep,\Qry)$ be defined as follows.  Fix non-empty set ~$\univ$ and integers $k,m,n>0$.  Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.  The $\Hash$ algorithm samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [k]$.  The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones. The following result shows, informally, that if~$F$ is a good PRF and the (non-adaptive) FP rate is sufficiently small, then $B_\mathrm{lin}$ is secure against adaptive FP-finding adversaries.

\fixme{Note: the following theorem is incorrect for $r>1$.  Or, at least, the proof does not cover $r>1$.}\acnote{Modified.}
\begin{theorem}\label{thm1}
Fix $k,m,n>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
Let~$A$ be an adversary, compatible with $\ExpFPSecHash{B_\mathrm{lin},r}{\cdot}$, that asks at most~$q$ queries in time $t$ to its $\QryOracle$ oracle.  Then 
\[
\AdvFPSecHash{B_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} +
\AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
for PRF-adversaries~$B_1$ and $B_2$ given explicitly in the proof of
this theorem. Here, $B_1$ and $B_2$, each ask $q$ oracle queries in time O(t). \tsnote{Statement about resources of these reductions.}
\end{theorem}
Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, non-adaptive) FP-probability for~$B_\mathrm{lin}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{r}$ arises as a result
of removing adaptivity.  Finally, $\dbinom{q}{r} \leq q^r$ (with
reasonable tightness when~$t$ is small) in which case the final term in the bound behaves as 
$(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
trying to find a single FP in each of~$r$ independent``rounds'', each round
consisting of~$q$ attempts.
%Before giving the proof, we note that  $(1-e^{-kn/m})^k \rightarrow 0$ as the ratio between the bit-length of the representation~$M$ and the size of the represented set~$S$, i.e.,$m/n$ tends to $\infty$.
%
\begin{proof}[\Cref{thm1}]
The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpFPSecHash{B_\mathrm{lin},r}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$. So,

@@

%\caption{$\Cref{thm1}:\game{5}(A)$ in game playing argument}\label{fig:game5}
\begin{figure}
\centering
\fpage{0.8}
{
\hpagess{0.5}{0.4}{
\underline{$\game{5}(A)$}\\
$c \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$\calY \gets \emptyset$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calY| < r$ or $\calY \cap \calS \neq \emptyset$ then\\
\nudge Ret 0\\
if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
$c \gets c+1$\\
if $c \in \mathcal{I}$ then\\
\nudge $\calY \gets \calY \cup {x}$\\
\nudge Ret~$1$\\\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{$\Cref{thm1}:\game{5}(A)$ in game playing argument}\label{fig:game5}
\end{figure}

@@

%\caption{Non-adaptive adversaries simulating $\game{2}(A)$} \label{AGame3}
\begin{figure}
\centering
\fpage{0.8}{
\hpagessl{.5}{.4}
{
$\adversaryv{D^{\HashOracle}}$\\
$c \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$\calY, \calZ \gets \emptyset $ \\
When $A$ asks $\QryOracle(x)$:\\
\nudge $c \gets c+1$\\
\nudge if $c \in \mathcal{I}$ then\\
\nudge \nudge $\calY \gets \calY \cup {x}$\\
\nudge \nudge Ret~$1$\\
\nudge else \\
\nudge  \nudge Ret~$0$\\
When $A$ halts with output $\calZ'$\\
\nudge if $|\calZ'|<r \, \mbox{or} \, |\calY| < r$\\
\nudge \nudge Ret $\emptyset$\\
\nudge if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
\nudge \nudge Ret $\calY$\\
\nudge Ret $\emptyset$\\\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
{
$\adversaryv{D'^{\HashOracle}}$\\
$c \gets 0$\\
$\ell \getsr [q]$\\
%$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$\calY \gets \emptyset$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge c \gets c + 1$\\
\nudge if $c == \ell$\\
$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
$\nudge$ $\nudge \calY \gets \calY \cup {x}$\\
\nudge else\\
$\nudge$ $\nudge r \gets 0$\\
\nudge Ret $r$\\
When $A$ halts with output $\calZ'$\\
\nudge $z \gets \calY$\\
\nudge if $\Qry^{\HashOracle}(M,z)=1$ then\\
\nudge \nudge Ret $z$\\
\nudge else\\
\nudge \nudge Ret Null\\\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Non-adaptive adversaries simulating $\game{3}(A)$} \label{fig:AGame3}
\end{figure}

>>>>

\heading{Linear-PRF construction. }
Here we consider a hash-based filter that was attacked by Neidermayer et al. in~\cite{xxx}.  Let $B_{\mathrm{lin}}=(\Hash,\Rep,\Qry)$ be defined as follows.  Fix non-empty set ~$\univ$ and integers $k,m,n>0$.  Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.  The $\Hash$ algorithm samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [1,k]$.  The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones. The following result shows, informally, that if~$F$ is a good PRF and the (non-adaptive) FP rate is sufficiently small, then $B_\mathrm{lin}$ is secure against adaptive FP-finding adversaries.

\fixme{Note: the following theorem is incorrect for $r>1$.  Or, at least, the proof does not cover $r>1$.}\acnote{Modified.}
\begin{theorem}\label{thm1}
Fix $k,m,n>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
Let~$A$ be an adversary, compatible with $\ExpFPSecHash{B_\mathrm{lin},r}{\cdot}$, that asks at most~$q$ queries in time $t$ to its $\QryOracle$ oracle.  Then 
\[
\AdvFPSecHash{B_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
for PRF-adversaries~$B_1$ and $B_2$ given explicitly in the proof of
this theorem. Here, $B_1$ and $B_2$, each ask $q$ oracle queries in time O(t). \tsnote{Statement about resources of these reductions.}
\end{theorem}
Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, non-adaptive) FP-probability for~$B_\mathrm{lin}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{r}$ arises as a result
of removing adaptivity.  Finally, $\dbinom{q}{r} \leq q^r$ (with
reasonable tightness when~$r$ is small) in which case the final term in the bound behaves as 
$(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
trying to find a single FP in each of~$r$ independent``rounds'', each round
consisting of~$q$ attempts.
%Before giving the proof, we note that  $(1-e^{-kn/m})^k \rightarrow 0$ as the ratio between the bit-length of the representation~$M$ and the size of the represented set~$S$, i.e.,$m/n$ tends to $\infty$.
%
\begin{proof}[\Cref{thm1}]
The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpFPSecHash{B_\mathrm{lin},r}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$. So,

@@

%\caption{$\Cref{thm1}:\game{5}(A)$ in game playing argument}\label{fig:game5}
\begin{figure}
\centering
\fpage{0.8}
{
\hpagess{0.5}{0.4}{
\underline{$\game{5}(A)$}\\
$c \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$\calY \gets \emptyset$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calY| < r$ or $\calY \cap \calS \neq \emptyset$ then\\
\nudge Ret 0\\
if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
$c \gets c+1$\\
if $c \in \mathcal{I}$ then\\
\nudge $\calY \gets \calY \cup {x}$\\
\nudge Ret 1\\
else\\
\nudge Ret 0 \\\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm1}:$\game{5}(A)$ in game playing argument}\label{fig:game5}
\end{figure}

@@

%\caption{Non-adaptive adversaries simulating $\game{2}(A)$} \label{AGame3}
\begin{figure}
\centering
\fpage{0.8}{
\hpagessl{.5}{.4}
{
$\adversaryv{D^{\HashOracle}}$\\
$c \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$\calY, \calZ \gets \emptyset $ \\
When $A$ asks $\QryOracle(x)$:\\
\nudge $c \gets c+1$\\
\nudge if $c \in \mathcal{I}$ then\\
\nudge \nudge $\calY \gets \calY \cup {x}$\\
\nudge \nudge Ret~$1$\\
\nudge else \\
\nudge  \nudge Ret~$0$\\
When $A$ halts with output $\calZ'$\\
\nudge if $|\calZ'|<r \, \mbox{or} \, |\calY| < r$\\
\nudge \nudge Ret $\emptyset$\\
\nudge if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
\nudge \nudge Ret $\calY$\\
\nudge Ret $\emptyset$\\\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
{
$\adversaryv{D'^{\HashOracle}}$\\
$c \gets 0$\\
$\ell \getsr [q]$\\
%$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$\calY \gets \emptyset$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge c \gets c + 1$\\
\nudge if $c == \ell$\\
$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
$\nudge$ $\nudge \calY \gets \calY \cup {x}$\\
\nudge else\\
$\nudge$ $\nudge r \gets 0$\\
\nudge Ret $r$\\
When $A$ halts with output $\calZ'$\\
\nudge $z \gets \calY$\\
\nudge if $\Qry^{\HashOracle}(M,z)=1$ then\\
\nudge \nudge Ret $z$\\
\nudge else\\
\nudge \nudge Ret $\lambda$\\\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Non-adaptive adversaries simulating $\game{3}(A)$} \label{fig:AGame3}
\end{figure}
